The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-07-11 paper.tex
Completed Sonority Rise section

>>>>

\subsection{Sonority Rise}

I will contrast {\sc Sonority Angle} with an alternative metric of sonority contour faithfulness proposed by \citet{flemming.2008}, {\sc Sonority Rise}, which takes the ratio of the underlying sonority contour /C\textsubscript{1}C\textsubscript{2}/ and the surface contour [C\textsubscript{1}V].

   \ex. \textsc{Sonority Rise} = $1-\frac{C_2-C_1}{V-C_1}$

The following sample calculations illustrate how \textsc{SonRise} distance is computed:

\ex.    \begin{center}
    \begin{tabular}{c c | c c | c}
    C\textsubscript{1}C\textsubscript{2}   & Rise & C\textsubscript{1}V & Rise & \textsc{SonRise} Distance\\ \hline
    NT &  -2  &  N\textipa{1}T & 3 & $1-\frac{1-3}{6-3}=1.7$ \\
    TT &  0   &  T\textipa{1}T & 5 & $1-\frac{1-1}{6-1}=1.0$ \\
    TN &  2   &  T{\textipa{1}}N & 5 & $1-\frac{3-1}{6-1}=0.6$ \\ 
    \end{tabular}
    \end{center}

As with {\sc Sonority Angle}, this gives rise to a family of constraints {\sc Ident(SonRise)}$<n$, defined similarly to {\sc Ident(SonAngle)}$<n$.

{\sc Sonority Rise} also gives rise to a hierarchy of susceptbility of clusters.

\ex. {\sc Sonority Rise} hierarchy

\vspace{-3em}
\noindent \resizebox{\linewidth}{!}{\usebox{\sonorityrisehierarchycompressed}}

Though in many ways similar to the {\sc Sonority Angle} hierarchy, it makes several crucially different predictions. For example, it does not share the prediction of {\sc Sonority Angle} that RN is the most likely of the falling sonority clusters to epenthesise -- rather, if RN undergoes epenthesis then we expect FT and NF to do the same. Furthermore, it predicts that if NT and RT fail to undergo epenthesis due to the high faithfulness cost of interrupting these clusters, then RF should also fail to undergo epenthesis.
